### 2023-06-09 README.Rmd
update 230609_v01a

---
output: github_document
bibliography: references.bib
---

@@

# validateHOT &#127919;

<!-- badges: start -->
<!-- badges: end -->

The goal of validateHOT is to validate the results of your validation task (also known as holdout task). A validation task is essential to make sure that your collected data of a *MaxDiff*, *CBC*, or *ACBC* are valid and can also predict outside task that were **not** included in estimating your utility scores. At the moment, <code>validateHOT</code>
provides functions for 3 key areas:

<ul>
<li>validation metrics mainly reported in preference measurement
studies</li>

@@

<ul> <li><code>hitrate</code>: </li>

<li><code>mhp</code>: </li>

<li><code>kl</code>: </li>

<li><code>mae</code>: </li>

<li><code>medae</code>: </li>

<li><code>mhp</code>: </li>

<li><code>rmse</code>: </li>

@@

<li><code>accuracy</code>: </li>

<li><code>f1</code>: </li>

<li><code>precision</code>: </li>

<li><code>recall</code>: </li>

<li><code>specificity</code>: </li>

@@

<li><code>freqassort</code>: </li>

<li><code>reach</code>: </li>

<li><code>shareofpref</code>: </li>

@@

<li><code>ACBC_interpolate</code>: </li>

<li><code>ACBC</code>: </li>

<li><code>CBC_lin</code>: </li>

<li><code>CBC</code>: </li>

<li><code>MaxDiff</code>: </li>

@@

<ul>
<li>
<code>createHOT</code>: creates the validation/holdout task for you. For example, in a *CBC* the total utilities are calculated by the sum of each attribute level. You have to specify the attribute levels for each alternative in the validation/holdout task and it will calculate the total utility for each alternative in the validation/holdout task.
</li>
<li>
<code>accuracy</code>: generates the number of correct predicted choice or no-choice divided by the total number of predictions. Only possible for a binary output, e.g., buy vs. no-buy correctly predicted.
</li>
<li>
<code>f1</code>: generates the F1-Score. F1-Score is calculated by the following formula $\frac{2 * precision * recall}{precision + recall}$. Only possible for a binary output, e.g., buy vs. no-buy correctly predicted.
</li>
</ul>

>>>>

---
output: github_document
bibliography: references.bib
editor_options: 
  markdown: 
    wrap: 72
---

@@

# validateHOT 🎯

<!-- badges: start -->

<!-- badges: end -->

The goal of validateHOT is to validate the results of your validation
task (also known as holdout task). A validation task is essential to
make sure that your collected data of a *MaxDiff*, *CBC*, or *ACBC* are
valid and can also predict outside task that were **not** included in
estimating your utility scores. Although commercial studies often do not
include a validation/holdout task [@yang2018], it is highly recommended
to do so [@Orme.2015; @rao2014a]. This validation/ holdout task does not
only help to check whether everything went right during data collection
but also to determine your final model. <code>validatHOT</code> provides
some of the relevant metrics to test the performance of your data in
predicting a holdout task. In [Sawtooth
Software's](https://sawtoothsoftware.com/) *CBC* a fixed validation/
holdout task is automatically implemented. If you conduct a *MaxDiff* or
*ACBC* study these have to be programmed by yourself.

👉🏾 <u>What you need to provide</u>: <br> After collecting your data, and
running your initial *Hierarchical Bayes* models, you can turn to
<code>validateHOT</code> and test how good your model predicts choices
in the validation/ holdout task. Herefore, you only have to insert your
**raw** utility scores as well as the actual choice of your validation/
holdout task. You can use the <code>merge()</code> provided by
<code>base</code> package [@base]. Afterward, you can read in your data
file and enjoy <code>validateHOT</code>.

👈🏾 <u>What you get</u>:<br> At the moment, <code>validateHOT</code>
provides functions for 3 key areas:

<li>validation metrics mainly reported in preference measurement
studies</li>

@@

<li><code>hitrate</code>: creates the *Hit Rate* (correctly predicted
choices) of your validation task. The output will contain the chance
level in your validation task ($\frac{1}{alternatives}$) in percentage.
The number of correctly predicted partcipants' choices as well as the
percentage of how many choices were correctly predicted. If you specify
an optional <code>Group</code> argument the output is split by
groups.</li>

<li><code>kl</code>: Kullback-Leibler-Divergence ?????? [@ding2011]. If
you specify an optional <code>Group</code> argument the output is split
by groups.</li>

<li><code>mhp</code>: averaged hit probability of participant's actual
choice in the validation/ holdout task. If you specify an optional
<code>Group</code> argument the output is split by groups.</li>

<li><code>mae</code>: average absolute error, i.e., deviation between
predicted and stated choice share. If you specify an optional
<code>Group</code> argument the output is split by groups.</li>

<li><code>medae</code>: since the averaged absolute error can be highly
influenced by the If you specify an optional <code>Group</code> argument
the output is split by groups.</li>

<li><code>mhp</code>:</li>

<li><code>rmse</code>:</li>

@@

<li><code>accuracy</code>:</li>

<li><code>f1</code>:</li>

<li><code>precision</code>:</li>

<li><code>recall</code>:</li>

<li><code>specificity</code>:</li>

@@

<li><code>freqassort</code>:</li>

<li><code>reach</code>:</li>

<li><code>shareofpref</code>:</li>

@@

<li><code>ACBC_interpolate</code>:</li>

<li><code>ACBC</code>:</li>

<li><code>CBC_lin</code>:</li>

<li><code>CBC</code>:</li>

<li><code>MaxDiff</code>:</li>

@@

<li><code>createHOT</code>: creates the validation/holdout task for you.
For example, in a *CBC* the total utilities are calculated by the sum of
each attribute level. You have to specify the attribute levels for each
alternative in the validation/holdout task and it will calculate the
total utility for each alternative in the validation/holdout task.</li>

<li><code>accuracy</code>: generates the number of correct predicted
choice or no-choice divided by the total number of predictions. Only
possible for a binary output, e.g., buy vs. no-buy correctly
predicted.</li>

<li><code>f1</code>: generates the F1-Score. F1-Score is calculated by
the following formula
$\frac{2 * precision * recall}{precision + recall}$. Only possible for a
binary output, e.g., buy vs. no-buy correctly predicted.</li>

## Why <code>validateHOT</code>

comparison to Metrics

studi seminar für preference measurement techniques --\> often not
getting in touch with *R* before, so wanted to make it easier for them.
this
